Sequence classifications to facilitate designing an effective intervention of motivational interview

### 2017-03-03 paper/AMIA/main.tex
update discussion sections
update paper title

\title{Designing an effective intervention of motivational interview using sequence classification methods}

@@

Third, alternate sequences provide higher performance for all Markov models. Even, it provides highest precision and F-measure for alternate sequences. This indicates that each pair of alternate behavior codes forward their mutual information to the next step more accurately which improve performance for distinguishing outcomes of the motivational interview. And this is obvious because if we know the previous two behavior codes (e.g. provider's question and adolescent's answer) then it is easier to know the expected answer for the current question.

>>>>

\title{Sequence classifications to facilitate designing an effective intervention of motivational interview}

@@

Third, alternate sequences provide higher performance for all Markov models. Even, it provides highest precision and F-measure for general Markov model. This indicates that each pair of alternate behavior codes forward their mutual information to the next step more accurately which improve performance for distinguishing outcomes of the motivational interview. And this is obvious because if we know the previous two behavior codes (e.g. provider's question and adolescent's answer) then it is easier to know the expected answer for the current question.
